\documentclass[margin]{res}

\setlength{\textwidth}{5in}

\usepackage{layout}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\hypersetup{colorlinks=true, urlcolor=blue}

\usepackage[sorting=ydnt,style=numeric, giveninits=true, maxbibnames=40]{biblatex}
\addbibresource{talibov-cv.bib}

\textheight=700pt

\begin{document}

    \moveleft.5\hoffset\centerline{\large\bf Vladimir O. Talibov}
    \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
    \moveleft.5\hoffset\centerline{Last update: \today}
    \moveleft.5\hoffset\centerline{Småbrukets backe 31 \hfill \href{mailto:vladimir.o.talibov@gmail.com}{vladimir.o.talibov@gmail.com}}
    \moveleft.5\hoffset\centerline{SE 141 58, Huddinge, Sweden \hfill}
    
    \begin{resume}
      
        \section{Summary}{Biochemist with a passion for target-based drug discovery. I like to keep a bridge between physical chemistry and protein science. Experienced in kinetic and biophysical methods.}
    
        \section{Skills}

        {\sl \underline{Experimental:}} Biochemical assays, biophysical methods (SPR biosensors, ITC, TSA), enzymology, protein techniques, expression\&purification, automation, protein crystallography\\
        {\sl \underline{Computer:}} Analysis suits and their integration, Linux, KNIME, \TeX, ELN, LIMS\\
%        {\sl \underline{Languages:}} English, Russian, Swedish (basic)\\
        {\sl \underline{Expertise:}} Enzymology, assay development, biophysical methods, small molecules.
    
        \section{Experience} 
        
            {\sl Associate Principal Scientist, Senior Scientist} \hfill Mar 2021 -- current \\
            Sprint Bioscience AB, Huddinge, Sweden
            \begin{itemize}
            \setlength\itemsep{0em}
            \item Biochemical and biophysical methods in DMTA cycle
            \item Support of FBLD projects as a member of Protein Science team
            \item Protein biochemistry.
            \end{itemize}
            
            {\sl Researcher} \hfill Aug 2019 -- Feb 2021 \\
            MAX IV Laboratory, Lund, Sweden
            \begin{itemize}
            \setlength\itemsep{0em}
            \item Operation protocols of core fragment screening facility
            \item Design, curation and maintenance of in-house fragment library
            \item BioMAX user support as a beamline scientist, including on-call service.
            \end{itemize}
            
            {\sl PhD student, Researcher} \hfill Apr 2014 -- Jun 2019 \\
            Uppsala University, Uppsala, Sweden
            \begin{itemize}
            \setlength\itemsep{0em}
            \item Development of biophysical and enzymatic assays for ligand discovery
            \item Maintenance of biosensors and chromatographic equipment
            \item Teaching (20\%, MSc-level courses).
            \end{itemize}
            
            {\sl Laboratory Assistant} \hfill Jul 2012 -- Feb 2014 \\
            OOO "Biochip-IMB", Moscow, Russia
            \begin{itemize}
            \setlength\itemsep{0em}
            \item Validation of multiplex clinical diagnostics assays
            \item QC of proteins, synthetic oligonucleotides and reactive small molecules.
            \end{itemize}
         
        \section{Education} 

            {\sl PhD in Biochemistry} \hfill 2014 -- 2019 \\
            Uppsala University, Uppsala, Sweden \\
            Advisor: Prof. U. Helena Danielson \\
            \href{http://uu.diva-portal.org/smash/record.jsf?pid=diva2%3A1256395&dswid=214}{"Interaction kinetic analysis in drug design, enzymology and protein research"}.
            
            {\sl BSc\&MSc in Chemistry} \hfill 2008 -- 2013 \\
            Moscow State University, Moscow, Russia \\
            Specialisation in bioorganic chemistry.
                        
        \section{Interests} Molecular recognition, assay technology, early stage drug discovery, mechanistic characterization.
        
        \section{Publications}

            \nocite{*}
            h-index - 9, research articles - 13; details are available at \href{https://scholar.google.com/citations?hl=sv&user=H5uK2zsAAAAJ&view_op=list_works&authuser=2&sortby=pubdate}{GScholar}.\\
            Other: reviews - 2, book chapters - 1, patents - 1.\\
            
            % Uncomment to print bibliography
            % \printbibliography[heading=none]

    \end{resume}

\end{document}
